\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-01-29 paper/main.tex
.

\subtitle{Subject Section}

\title[short Title]{Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction}
\author[Sample \textit{et~al}.]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert Hoehndorf\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
$^{\text{\sf 2}}$Department, Institution, City, Post Code,
Country.}

@@

\subsection{High level description}
Our aim is to develop and evaluate a computational model to predict
drug--target interactions. Specifically, given a protein, we are
interested in identifying the drugs that may target the protein; this
scenario is motivated by the need to identify drugs that can target a
specific protein that may be associated with a disease or abnormal
phenotypes.
Our aim is further to combine two different types of features:
structural information based on protein structure and the

@@

	\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|r|}
		\hline
		Approach&Splitting scheme&Original AUROC score&Protein split AUROC&MicroAUC\\
		\hline
		DTINet&DP pairs&$91$&$84.1$&$67.2$\\
		DTIGEMS+&DP pairs&$93$& $72.2$& $67.8$ \\
		DTI-CDF&Proteins&$83$&$83$&$79$\\
		\hline
	\end{tabular}
	\item A naive predictor (ranking proteins) and predict each drug similarly achieves cutting edge performance ($87.5$ AUROC for whole dataset, $85.5$ for 5-fold cross validation in drug-split) $\rightarrow$ No prot focused microAUC possible. $\rightarrow$ hub proteins
	\item Yamanishi Dataset is only partially suitable \todo{for
            comparing results}}, if everybody just derives a suitable subset (DTIGEMS)
	\item This also applies to drug target affinity prediction. We were hereby able to roughly reproduce the results from MolTrans (Bioinformatics) on BioSnap

>>>>

\subtitle{Subject Section}
\newcommand{\name}{Voodoo }

\title[short Title]{\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction}
\author[Sample \textit{et~al}.]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert Hoehndorf\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
$^{\text{\sf 2}}$Department, Institution, City, Post Code,
Country.}

@@

\subsection{\name identifies drugs that target a protein}

We developed \name as a computational model to predict drug--target
interactions. Specifically, given a protein, \name will identify and
rank drugs that likely target this protein. \name combines two 
types of features: structural information for drugs and proteins that
can be used to determine if they may physically interact, and

This scenario is motivated by the need to identify drugs that can target a
specific protein that may be associated with a disease or abnormal
phenotypes.
Our aim is further to combine two different types of features:
structural information based on protein structure and the

@@

	\begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|r|}
		\hline
		Approach&Splitting scheme&Original AUROC score&Protein split AUROC&MicroAUC\\
		\hline
		DTINet&DP pairs&$91$&$84.1$&$67.2$\\
		DTIGEMS+&DP pairs&$93$& $72.2$& $67.8$ \\
		DTI-CDF&Proteins&$83$&$83$&$79$\\
		\hline
	\end{tabular}
	\item A naive predictor (ranking proteins) and predict each drug similarly achieves cutting edge performance ($87.5$ AUROC for whole dataset, $85.5$ for 5-fold cross validation in drug-split) $\rightarrow$ No prot focused microAUC possible. $\rightarrow$ hub proteins
	\item Yamanishi Dataset is only partially suitable \todo{for
            comparing results}, if everybody just derives a suitable subset (DTIGEMS)
	\item This also applies to drug target affinity prediction. We were hereby able to roughly reproduce the results from MolTrans (Bioinformatics) on BioSnap
